fishtraits

### 2019-09-03 data-raw/web_scrape.Rmd
clean up

Choose FID and Genus
```{r}

for (i in 6:length(fid_text)) {
  #select and search the FID dropdown
  fid <- rd$findElement(using = 'css selector', "#fid-combo")
  fid$clearElement()
  #pass to search box
  print(fid_text[i])
  fid$sendKeysToElement(list(fid_text[i]))
  #click matching one
  Sys.sleep(0.15)
  clickObject("#ui-id-1")

  #get list of Genus's that are now possible
  clickObject(".ui-combobox2 .ui-icon-triangle-1-s")
  Sys.sleep(0.15)
  genus_list <- rd$findElement('css selector', '#ui-id-2')
  genus_text <- unlist(strsplit(unlist(genus_list$getElementText()), "\n"))
  print(genus_text)

@@

    #make sure the appropriate column boxes are checked
    # columns <- rd$findElement(using = 'css selector', '#ui-accordion-ac1-header-1')
    # columns$clickElement()
    # 
    #selectors for all boxes that need to be checked

@@

Pick the columns we want
```{r}

```

Submit search and download
```{r}

```

>>>>

Choose FID and Genus. All the boxes under the "columns" header unfortunately need to be checked manually because css selectors couldn't be identified for each individual box. Only have to do it once though!
```{r}

for (i in 1:length(fid_text)) {
  #select and search the FID dropdown
  fid <- rd$findElement(using = 'css selector', "#fid-combo")
  fid$clearElement()
  #pass to search box
  print(fid_text[i])
  fid$sendKeysToElement(list(fid_text[i]))
  #click matching one
  Sys.sleep(0.25)
  clickObject("#ui-id-1")

  #get list of Genus's that are now possible
  clickObject(".ui-combobox2 .ui-icon-triangle-1-s")
  Sys.sleep(0.25)
  genus_list <- rd$findElement('css selector', '#ui-id-2')
  genus_text <- unlist(strsplit(unlist(genus_list$getElementText()), "\n"))
  print(genus_text)

@@

@@
